### 2017-02-27 paper/chapters/gan.tex
fixed captions (short caption)

\begin{figure}[htb]
\centering
\includestandalone[width=\textwidth,mode=buildnew]{media/gan_conceptual}
  \caption{Architecture used for generative adversarial networks}
  \label{fig:gan_a}
  \medskip
  \small
  The above figure illustrates the computational graph and gradient flow in the GAN framework.\\
  $X$ denotes the dataset containing real-world data sampled from $p_{data}$, which we aim to model.\\
  Solid arrows indicate the forward pass in the model while dashed arrows denote the gradient flow during a backward pass.
\end{figure}

@@

\begin{figure}[htb]
\centering
  \includegraphics[width=\linewidth]{media/gan_training-crop}
  \caption{Learning a GAN on a one-dimensional distribution from the original paper\cite{gan:2014}}
  \label{fig:gan_training}
  \medskip
  \small
  The line named $z$ denotes the noise prior, while the arrows to the line indicated by $x$ is the transformation learned by the generator network. Three different distributions are showed, the solid line represents the generated sample in each step, while the dots are sampled from the data distribution $p_{data}(x)$. The dashed line shows the decision boundary with which probability the discriminator can distinguish between real and fake data.\\
  (a) Prior to training when both $D$ and $G$ are poor and $p_{model}$ does not match $p_{data}$.\\
  (b) After a step of learning $D$ with fixed $G$, the discriminator is able to distinguish fake from real samples easily as indicated by the decision boundary.\\
  (c) After a step of learning $G$ with fixed $D$ has the generator learned to produce samples more similar to $p_{data}(x)$.\\
  (d) The model has reached the nash equilibrium where $p_{model} = p_{data}$ and the discriminator can only distinguish between real and fake sample with $p=0.5$.
\end{figure}

@@

\begin{figure}[t]
\centering
  \includegraphics[width=\linewidth]{media/dcgan_vector}
  \caption{Vector arithmetic performed in latent space $z$, from DCGAN paper\cite{dcgan:2015}}
  \label{fig:dcgan_vector}
  \medskip
  \small
\end{figure}

@@

\begin{figure}[t]
\centering
  \includegraphics[width=\linewidth]{media/bedroom_scenes-crop}
  \caption{Bedroom scenes generated by the DCGAN model, from the original paper\cite{lapgan:2015}}
  \label{fig:lapgan}
  \medskip
  \small
\end{figure}
Laplacian Generative Adversarial Networks (LAPGAN) \cite{lapgan:2015} are an extension to GANs applied to images using laplacian pyramids \cite{laplacian:1983}.
Instead of using a single generator network, LAPGAN uses a series of deep convolutional networks as generators where each generator receives the output of the previous generator.

>>>>

\begin{figure}[htb]
\centering
\includestandalone[width=\textwidth,mode=buildnew]{media/gan_conceptual}
  \caption[GAN Architecture]{Architecture used for generative adversarial networks}
  \label{fig:gan_a}
  \medskip
  \small
  The above figure illustrates the computational graph and gradient flow in the GAN framework.\\
  $X$ denotes the dataset containing real-world data sampled from $p_{data}$, which we aim to model.\\
  Solid arrows indicate the forward pass in the model while dashed arrows denote the gradient flow during a backward pass.
\end{figure}

@@

\begin{figure}[htb]
\centering
  \includegraphics[width=\linewidth]{media/gan_training-crop}
  \caption[Learning Procedure in a GAN]{Learning a GAN on a one-dimensional distribution from the original paper\cite{gan:2014}}
  \label{fig:gan_training}
  \medskip
  \small
  The line named $z$ denotes the noise prior, while the arrows to the line indicated by $x$ is the transformation learned by the generator network. Three different distributions are showed, the solid line represents the generated sample in each step, while the dots are sampled from the data distribution $p_{data}(x)$. The dashed line shows the decision boundary with which probability the discriminator can distinguish between real and fake data.\\
  (a) Prior to training when both $D$ and $G$ are poor and $p_{model}$ does not match $p_{data}$.\\
  (b) After a step of learning $D$ with fixed $G$, the discriminator is able to distinguish fake from real samples easily as indicated by the decision boundary.\\
  (c) After a step of learning $G$ with fixed $D$ has the generator learned to produce samples more similar to $p_{data}(x)$.\\
  (d) The model has reached the nash equilibrium where $p_{model} = p_{data}$ and the discriminator can only distinguish between real and fake sample with $p=0.5$.
\end{figure}

@@

\begin{figure}[t]
\centering
  \includegraphics[width=\linewidth]{media/dcgan_vector}
  \caption[Vector arithmetic in DCGAN]{Vector arithmetic performed in latent space $z$, from DCGAN paper\cite{dcgan:2015}}
  \label{fig:dcgan_vector}
  \medskip
  \small
\end{figure}

@@

\begin{figure}[t]
\centering
  \includegraphics[width=\linewidth]{media/bedroom_scenes-crop}
  \caption[Generated Samples by DCGAN]{Bedroom scenes generated by the DCGAN model, from the original paper\cite{lapgan:2015}}
  \label{fig:lapgan}
  \medskip
  \small
\end{figure}
Laplacian Generative Adversarial Networks (LAPGAN) \cite{lapgan:2015} are an extension to GANs applied to images using laplacian pyramids \cite{laplacian:1983}.
Instead of using a single generator network, LAPGAN uses a series of deep convolutional networks as generators where each generator receives the output of the previous generator.

### 2017-02-27 paper/chapters/vae.tex
replace explicit kl div eq by expectation
improve iwae citation (in title, oops)
fixed captions (short caption)

\begin{figure}[h]
  \centering
  \includestandalone[width=\linewidth,mode=buildnew]{media/vae_conceptual}
  \caption{simplified VAE architecture using a gaussian prior on $z$}
  \label{fig:vae_architecture}
\end{figure}

@@

\subsubsection{Kullback-Leibler Divergence}
In order to approximate one distribution $Q$ to another distribution $P$, there needs to be a measurement of how close $Q$ is to $P$.
One commonly used measurement is called Kullback-Leibler (KL) divergence\cite{kl_div:1951} which enables the variational inference methods to choose appropiate distributions.
%\paragraph{The Kullback-Leibler Divergence} (KL divergence) is a measurement for the difference between two probability distributions. $\mathcal{D}_{\mathrm{KL}}(P \| Q)$ can informally described as the amount of information which is lost when using $Q$ to represent $P$.
The KL divergence from $Q$ to $P$ is defined in Equation \ref{eq:kl_div}.
\begin{equation}
  \label{eq:kl_div_disc}
  \mathcal{D}_{\mathrm{KL}}(P || Q) = \sum_{i} P(i) \log \frac{P(i)}{Q(i)}
\end{equation}
For continuous distributions $P$ and $Q$ the KL divergence is defined similarly in equation \ref{eq:kl_div_cont}.
\begin{equation}
  \label{eq:kl_div_cont}
  \mathcal{D}_{\mathrm{KL}}(P || Q) = \int P(i) \log \frac{P(i)}{Q(i)} di
\end{equation}

@@

    \subcaptionbox{with reparameterization applied}{\includestandalone[height=0.4\linewidth]{media/reparameterization_trick_with}}\\
  \end{tabular}
  \caption{reparameterization trick}
  \label{fig:rep_trick}
  \medskip
  \small
  Function $f_\theta(x)$ with inputs $x$ and (variational) parameters $\theta$ as computational graph.
  Left without and on the right with the reparameterization trick applied.\\
  Solid arrows show the forward pass and dashed arrows the error backpropagation using gradients.
  Rectangular nodes represent deterministic functions while circles indicate stochastic variables.
  %Note that backpropagation of gradients through stochastic nodes is problematic and adds bias (verify!)
\end{figure}

@@

\subsubsection{Conditional VAE \cite{cvae:2014} \cite{cvae_2:2015}}
\label{ssub:cvae}
\input{chapters/vae/cvae}

>>>>

\begin{figure}[h]
  \centering
  \includestandalone[width=\linewidth,mode=buildnew]{media/vae_conceptual}
  \caption[VAE architecture]{simplified VAE architecture using a gaussian prior on $z$}
  \label{fig:vae_architecture}
\end{figure}

@@

\subsubsection{Kullback-Leibler Divergence}
In order to approximate one distribution $Q$ to another distribution $P$, there needs to be a measurement of how close $Q$ is to $P$.
One commonly used measurement is called Kullback-Leibler (KL) divergence\cite{kl_div:1951} which enables the variational inference methods to choose appropiate distributions.
%\paragraph{The Kullback-Leibler Divergence} (KL divergence) is a measurement for the difference between two probability distributions. $\mathcal{D}_{\mathrm{KL}}(P \| Q)$ can informally described as the amount of information which is lost when using $Q$ to represent $P$.
The KL divergence from $Q$ to $P$ is defined in Equation \ref{eq:kl_div}.
\begin{equation}
  \label{eq:kl_div}
  \mathcal{D}_{\mathrm{KL}}(P || Q) = \mathbb{E}_{x \sim P(x)}\bigg[log \frac{P(x)}{Q(x)}\bigg]
\end{equation}
\todo[inline]{Add some description to the equation above, logarithmic difference between P and Q, bla bla expectation}
%For discrete probability distributions $P$ and $Q$, the KL divergence from $Q$ to $P$ is defined\cite{kl_div:1951} in equation \ref{eq:kl_div_disc}:
%\begin{equation}
  %\label{eq:kl_div_disc}
  %\mathcal{D}_{\mathrm{KL}}(P || Q) = \sum_{i} P(i) \log \frac{P(i)}{Q(i)}
%\end{equation}
%For continuous distributions $P$ and $Q$ the KL divergence is defined similarly in equation \ref{eq:kl_div_cont}.
%\begin{equation}
  %\label{eq:kl_div_cont}
  %\mathcal{D}_{\mathrm{KL}}(P || Q) = \int P(i) \log \frac{P(i)}{Q(i)} di
%\end{equation}

@@

    \subcaptionbox{with reparameterization applied}{\includestandalone[height=0.4\linewidth]{media/reparameterization_trick_with}}\\
  \end{tabular}
  \caption{Reparameterization Trick}
  \label{fig:rep_trick}
  \medskip
  \small
  Function $f_\theta(x)$ with inputs $x$ and (variational) parameters $\theta$ as computational graph.
  Left without and on the right with the reparameterization trick applied.\\
  Solid arrows show the forward pass and dashed arrows the error backpropagation using gradients.
  Rectangular nodes represent deterministic functions while circles indicate stochastic variables.
  %Note that backpropagation of gradients through stochastic nodes is problematic and adds bias (verify!)
\end{figure}

@@

\subsubsection{Conditional VAE}
\label{ssub:cvae}
\input{chapters/vae/cvae}
